---
title: "FastLinear-Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FastLinear-Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Introduction
The `FastLinear` package provides efficient linear regression functions using QR decomposition. This vignette demonstrates the usage of `fast_lm` and compares its performance and accuracy with the base R function `lm()`.

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(repos = c(CRAN = "https://cloud.r-project.org"))
library(devtools)
library(FastLinear) 
library(ggplot2)
library(bench)
```

```{r}
devtools::load_all()
```
## Example
We'll simulate a dataset with 1,000 observations and 10 predictors.
```{r}
set.seed(123)
n <- 10000
p <- 10
X <- matrix(rnorm(n * p), ncol = p)
beta_true <- rnorm(p + 1)  
y <- cbind(1, X) %*% beta_true + rnorm(n)

```
## Fitting models
Using fast_lm
```{r}
model_fast <- fast_lm(X, y)
summary(model_fast)

```
Using lm()
```{r}
data <- data.frame(y = y, X)
model_lm <- lm(y ~ ., data = data)
summary(model_lm)

```
## Comparing Results
# Correctness
We compare the coefficients from both models using all.equal().
```{r}
# Fit models
model_fast <- fast_lm(X, y)
data <- data.frame(y = y, X)
model_lm <- lm(y ~ ., data = data)

# Extract coefficients
coefficients_fast <- as.numeric(model_fast$coefficients)
coefficients_lm <- coef(model_lm)

# Assign names to coefficients_fast if missing
if (is.null(names(coefficients_fast))) {
  names(coefficients_fast) <- names(coefficients_lm)
}

# Ensure both are numeric vectors
coefficients_fast <- as.numeric(coefficients_fast)
coefficients_lm <- as.numeric(coefficients_lm)

# Compare the coefficients
comparison_result <- all.equal(coefficients_fast, coefficients_lm, tolerance = 1e-6)
print(comparison_result)


```
Interpretation: The coefficients are equal within a reasonable tolerance, demonstrating correctness.


# Efficiency
Benchmarking the performance of both functions using bench::mark().
```{r}
library(bench)
benchmark_results <- bench::mark(
  FastLinear = fast_lm(X, y),
  lm = lm(y ~ ., data = data),
  iterations = 100,
  check = FALSE
)

print(benchmark_results)

```
```{r}
autoplot(benchmark_results)

```
Interpretation: The fast_lm function is faster than lm(), demonstrating improved efficiency.



